The paper on blockchain front-running

### 2018-09-26 frontrunning/Latex/sections/paper.tex
fixed caption fonts

\begin{figure}[t]
\centering
\includegraphics[width=0.7\linewidth]{figures/Miner_reorder_frontrun.png}
\caption{\scriptsize The adversarial miner can monitor the Ethereum mempool for decentralized exchange cancel orders and upon seeing the cancellation transaction, he puts his buy order prior to the cancel transaction. Doing so, the miner can profit from the underlying trade and also get the gas included in the cancel transaction. \label{fig:MinerFrontrunning}} 
\end{figure}
%https://www.lucidchart.com/invitations/accept/c8768786-4a3f-4c78-b3c8-aa04a6b81d06

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.7\linewidth]{figures/Regular_frontrunning.png}
\caption{\scriptsize The Adversary up on seeing the Buy order, sends his own buy order with higher gas to front-run the first order. \label{fig:RegularFrontrunning}} 
\end{figure}
%https://www.lucidchart.com/invitations/accept/f8ca2662-5269-425d-9deb-deb14af2aac7

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.5\linewidth]{figures/Mining_pool_ratio.png}
\caption{\scriptsize The percentage of Ethereum blocks mined between block 3903900 and 3908029, this is the time frame in which Status.im ICO was running. This percentage roughly shows the hashing power ratio each miner had at that time. \label{fig:mining_pool_ratio}} % IS THIS STATEMENT CORRECT?
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{figures/Transactions_miners_while_status_ico_cut_only_icotx.png}
\caption{\scriptsize This chart shows the miners behaviour on the time window that Status.im ICO was running. It is clear that the number of successful transactions mined by F2Pool do not follow the random homogeneous pattern of the rest of the network. \label{fig:Transactions_miners_while_status_ico_cut}} 
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.7\linewidth]{figures/F2Pool_transactions_to_StatusICO_and_Refunds.png}
\caption{\scriptsize F2Pool prior to Status.im ICO deposited 100 Ether in multiple new Ethereum addresses. On the time of the ICO they sent these deposits to Status ICO smart contract and prioritized mining of these transactions in their mining pool, this was to overcome the dynamic ceiling algorithm of the token sale smart contract. Later on they sent the refunded Ether back to their own address. [Graph made using Blockseer.com] \label{fig:f2poolfront-run}}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{figures/Vulnerable_Loopring.png}
\caption{\scriptsize \emph{submitRing} Transaction in the old version of the Loopring protocol. Any user can regenerate this transaction by replacing the miner's address with his address and signing the hash of the ring using his private key. \label{fig:vulnerable_loopring}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/33d38ce9-4660-4743-806d-45c72f7e8393
\begin{figure}[t]
\centering
\includegraphics[width=0.7\linewidth]{figures/Dual_Authoring_Loopring.png}
\caption{\scriptsize \emph{submitRing} Transaction in the new version of the Loopring protocol. Other users cannot regenerate this transaction as they do not access auth-keys and hence are not able to create the signatures. \label{fig:not_vulnerable_loopring}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/8dee869c-482c-433f-a901-8d041a1dc526

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.5\linewidth]{figures/LibSubmarine.png}
\caption{\scriptsize Submarine Send~\cite{libsubmarine}. User generates an \textit{Unlock} transaction from which the commitment address is retrieved. By funding the \textit{commitment address}, user is committed to the unlock transaction. After the commitment transaction, in the reveal phase, user sends the \textit{reveal transaction} to the DApp and then after she can broadcast the Unlock transaction to unlock the funds in the commitment address. Finally after the "Auction'' is over, anyone can call \textit{Finalize} function to finalize the process.  \label{fig:LibSubmarine}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/3a259b74-1162-4fb5-8023-eb0311018295

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.7\linewidth]{figures/Miner_reorder_frontrun.png}
\caption{ The adversarial miner can monitor the Ethereum mempool for decentralized exchange cancel orders and upon seeing the cancellation transaction, he puts his buy order prior to the cancel transaction. Doing so, the miner can profit from the underlying trade and also get the gas included in the cancel transaction. \label{fig:MinerFrontrunning}} 
\end{figure}
%https://www.lucidchart.com/invitations/accept/c8768786-4a3f-4c78-b3c8-aa04a6b81d06

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.7\linewidth]{figures/Regular_frontrunning.png}
\caption{ The Adversary up on seeing the Buy order, sends his own buy order with higher gas to front-run the first order. \label{fig:RegularFrontrunning}} 
\end{figure}
%https://www.lucidchart.com/invitations/accept/f8ca2662-5269-425d-9deb-deb14af2aac7

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.5\linewidth]{figures/Mining_pool_ratio.png}
\caption{ The percentage of Ethereum blocks mined between block 3903900 and 3908029, this is the time frame in which Status.im ICO was running. This percentage roughly shows the hashing power ratio each miner had at that time. \label{fig:mining_pool_ratio}} % IS THIS STATEMENT CORRECT?
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{figures/Transactions_miners_while_status_ico_cut_only_icotx.png}
\caption{ This chart shows the miners behaviour on the time window that Status.im ICO was running. It is clear that the number of successful transactions mined by F2Pool do not follow the random homogeneous pattern of the rest of the network. \label{fig:Transactions_miners_while_status_ico_cut}} 
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.7\linewidth]{figures/F2Pool_transactions_to_StatusICO_and_Refunds.png}
\caption{ F2Pool prior to Status.im ICO deposited 100 Ether in multiple new Ethereum addresses. On the time of the ICO they sent these deposits to Status ICO smart contract and prioritized mining of these transactions in their mining pool, this was to overcome the dynamic ceiling algorithm of the token sale smart contract. Later on they sent the refunded Ether back to their own address. [Graph made using Blockseer.com] \label{fig:f2poolfront-run}}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{figures/Vulnerable_Loopring.png}
\caption{ \emph{submitRing} Transaction in the old version of the Loopring protocol. Any user can regenerate this transaction by replacing the miner's address with his address and signing the hash of the ring using his private key. \label{fig:vulnerable_loopring}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/33d38ce9-4660-4743-806d-45c72f7e8393
\begin{figure}[t]
\centering
\includegraphics[width=0.7\linewidth]{figures/Dual_Authoring_Loopring.png}
\caption{ \emph{submitRing} Transaction in the new version of the Loopring protocol. Other users cannot regenerate this transaction as they do not access auth-keys and hence are not able to create the signatures. \label{fig:not_vulnerable_loopring}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/8dee869c-482c-433f-a901-8d041a1dc526

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.5\linewidth]{figures/LibSubmarine.png}
\caption{ Submarine Send~\cite{libsubmarine}. User generates an \textit{Unlock} transaction from which the commitment address is retrieved. By funding the \textit{commitment address}, user is committed to the unlock transaction. After the commitment transaction, in the reveal phase, user sends the \textit{reveal transaction} to the DApp and then after she can broadcast the Unlock transaction to unlock the funds in the commitment address. Finally after the "Auction'' is over, anyone can call \textit{Finalize} function to finalize the process.  \label{fig:LibSubmarine}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/3a259b74-1162-4fb5-8023-eb0311018295
